---
title: "dogma"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{dogma}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dogma)
```

## Git hub repository

<https://github.com/rforbiodatascience25/group_21_package>

## Package description

This package illustrates the central dogma of molecular biology by generating random DNA sequences, transforming them into RNA, creating a list of codons from the RNA sequence, translating the codons into the protein sequence, and visualizing the counts of amino acids in the protein.

## Function description

#### Function one (generate_dna):

Generates random DNA sequence given desired length.

```{r}
set.seed(3)
generate_dna(10)
dna_seq <- generate_dna(50)
dna_seq
```

#### Function two (from_T_to_U):

This function takes a DNA sequence and transforms it to RNA.

```{r}
rna_seq <- dna_seq |> 
  from_T_to_U()
rna_seq
```

#### Function three (extract_codons):

The function takes a RNA sequence and creates a list of codons given the start position.

```{r}
codon_list <- rna_seq |> 
  extract_codons(start = 2)
codon_list
```

#### Function four (RNA_to_protein):

This function takes codon lists and outputs amino acid sequence.

```{r}
aa_seq <- codon_list |> 
  RNA_to_protein()
aa_seq
```

#### Function five (aa_barplot):

This function takes amino acid sequence and creates a bar plot of counts.

```{r}
aa_seq |> 
  aa_barplot()
```
